Dependent Object Types

### 2012-09-12 doc/candidacy/slides.tex
bump the slide numbers a bit up for projector to show them hopefully
typo
more refined intro

\useoutertheme{infolines}
\setbeamertemplate{headline}{}
\setbeamertemplate{footline}{
  \hfill
  \usebeamercolor[fg]{page number in head/foot}
  \usebeamerfont{page number in head/foot}
  \insertpagenumber\kern1em\vskip2pt
}
\setbeamertemplate{navigation symbols}{}

@@

\inputminted[fontsize=\footnotesize]{scala}{intro.scala}
\end{frame}

@@

\begin{frame}[fragile]{SML modules: Functions and Type Sharing}
\begin{minted}{sml}
functor mkDoubler(arg: X) :> X where type T = arg.T = struct
  type T = arg.T
  val v = arg.v
  val f = arg.f o arg.f
end

>>>>

\useoutertheme{infolines}
\setbeamertemplate{headline}{}
\setbeamertemplate{footline}{
  \hfill
  \usebeamercolor[fg]{page number in head/foot}
  \usebeamerfont{page number in head/foot}
  \insertpagenumber\kern1em\vskip10pt
}
\setbeamertemplate{navigation symbols}{}

@@

\begin{columns}
\begin{column}[t]{5cm}
\begin{minted}[fontsize=\footnotesize]{scala}
abstract class AbsCell {
  type T
  val init: T
  private var value: T = init
  def get = value
  def set(x: T) { value = x }
}

object Library {
  def update(c: AbsCell)(oldval: c.T, newval: c.T) =
    if (oldval == c.get) { c.set(newval); true }
    else false
}
\end{minted}
\end{column}
\begin{column}[t]{5cm}
\begin{minted}[fontsize=\footnotesize]{scala}
val c = new AbsCell {
  type T = Int
  val init = 1
}
c.set(2)
val a: AbsCell = c
// a.T is opaque
a.set(a.init)
\end{minted}
\end{column}
\end{columns}
\end{frame}

@@

\begin{frame}[fragile]{SML modules: Functors and Type Sharing}
\begin{minted}{sml}
functor mkDoubler(arg: X) :> X where type T = arg.T = struct
  type T = arg.T
  val v = arg.v
  val f = arg.f o arg.f
end
